Distributions in Carlson (2017)

### 2022-12-22 notebooks/Distributions_Carlson_2017.qmd
Corrects the computation of the probability for the simulations

```{r simulate}
params |> slice(1) |> get_cov_mat()
```

@@

```{r simulate-responses}
sim_responses <- sim_traits |>
  full_join(
    item_parameters          |>
      unnest(`Level admin.`) |>
      select(Item, `Level admin.`, d:a_2),
    by = c(level = "Level admin.")
  )        |>
  mutate(
    prob     = V1 * a_1 + V2 * a_2 + d,
    response = prob |> rbinom(n = n(), size = 1)
  )
```

>>>>

@@

```{r simulate-responses}
sim_responses <- sim_traits |>
  full_join(
    item_parameters          |>
      unnest(`Level admin.`) |>
      select(Item, `Level admin.`, d:a_2),
    by = c(level = "Level admin.")
  )        |>
  mutate(
    prob     = (1 + exp(- (V1 * a_1 + V2 * a_2 + d)))^(-1),
    response = prob |> rbinom(n = n(), size = 1)
  )
```
